Convolutional Neural Networks on Graphs\\ with Fast Localized Spectral Filtering

### 2016-10-29 nips2016/nips2016.tex
nips v8: small edition (Xavier) (2016-06-30)

The compositional local stationarity property of CNNs can be efficiently
implemented on regular grids, like image and sound domains, as convolutional and
downsampling operators are mathematically well-defined on such discretized
Euclidean spaces. This has led to the breakthrough of CNNs in image, video, and
sound recognition tasks \cite{art:LeCunBengioHinton15DL} as these data lie on
low-dimensional regular lattices. But not all data lie on regular grids. User
data on social networks, gene data on biological regulatory networks, log data
on telecommunication networks, or text documents on words' embedding are
important examples of data lying on irregular or non-Euclidean domains.
Unfortunately, CNNs cannot be directly applied to such complex domains.

A generalization to irregular grids is not straightforward as the building blocks of
CNNs, the convolution, the downsampling, and the pooling operators, cannot be directly applied to these domains. This makes this extension challenging, both theoretically and
implementation-wise. This work leverages the recent works of
\cite{pro:GregorLeCun10LRF, pro:CoatesNg11LRF,
art:BrunaZarembaSzlamLeCun13DLgraphs, art:HenaffBrunaLeCun15DLgraphs,
art:HammondVandergheynstGribonval11GraphWav,
art:ShumanNarangFrossardOrtegaVandergheynst13ReviewSPG} to introduce an
efficient implementation of CNNs on irregular domains represented here as
graphs. Graphs are universal representations of heterogeneous pairwise
relationships between possibly high-dimensional data. Graphs can encode complex
geometric structures, and can be studied with strong mathematical tools such as
spectral graph theory \cite{book:Chung97Spectral}, a blend between graph theory and harmonic analysis.

@@

\begin{table*}[h!]
\centering
\begin{tabular}{llc}
\toprule
Model & Architecture & Accuracy \\
\midrule
%Linear SVM & 91.76  \\
%Softmax & 92.36  \\
Classical CNN & C32-P4-C64-P4-FC512 & \textbf{99.20} \todo{99.33} \\
Proposed graph CNN & GC32-P4-GC64-P4-FC512 & 98.65 \todo{99.14} \\
\bottomrule
\end{tabular}
\caption{Classification accuracies for the proposed model and a classical CNN on
MNIST.} 
\label{tab:mnist}
\end{table*}

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{lc} \toprule
Model & Accuracy \\
\midrule
Linear SVM & 65.90 \\
Multinomial Naive Bayes & 68.51 \\
%Multinomial logistic regression (softmax) & 66.28 \\
Softmax & 66.28 \\
\addlinespace
FC2500 & 64.64 \\
FC2500-FC500 & 65.76 \\
\addlinespace
GC32 & 68.26 \\
GC32-FC500 & \todo{?} \\
\bottomrule \end{tabular}
\caption{Classification accuracies for the proposed model and a other algorithms
on 20NEWS.} 
\label{tab:20news}
\end{table*}

20NEWS consists of 18,846 (11,314 for training and 7,532 for testing) text
documents associated with 20 classes \cite{art:Joachims9620NEWS}. We extracted
the 10,000 most common words from the 93,953 unique words in this corpus. Each
document is represented using the bag-of-words model, normalized across words.
To test our model, we constructed a 16-NN graph of the word2vec
\cite{pro:MikolovChenCorradoDean13word2vec} embedding of those words, which
produced a graph of \todo{$n = |\V| = $ nodes (10k words and ? fake nodes) and
$|\E| = ?$ edges}.  All CNN models were trained for 20 epochs by the Adam
optimizer \cite{art:KingmaBa14AdamOpt} with a learning rate of 0.1, without regularization nor
dropout. The filter support was set to $K = 5$.

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{llccc} \toprule
& & \multicolumn{3}{c}{Accuracy} \\
\cmidrule{3-5}
Dataset & Architecture & Non-Param \eqnref{filt_non-param} &
Spline \eqnref{filt_spline} \cite{\bruna} &
Chebyshev \eqnref{filt_cheby} \\
\midrule
MNIST & GC10 & 95.75 & 97.26 & \textbf{97.48} \\
MNIST & GC32-P4-GC64-P4-FC512 & 96.28 & 97.15 & \textbf{98.65} \\
20NEWS & GC32 & \todo{?} & \todo{?} & \todo{?} \\
\bottomrule \end{tabular}
\caption{Comparison of accuracy results for different types of spectral filters.
Spline and Chebyshev filters use \todo{$K=20$}, \todo{$K=5$ for 20NEWS}.} 
\label{tab:filters}
\end{table*}

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{llccc} \toprule
& & \multicolumn{2}{c}{Time (ms)} & \\
Model & Architecture & CPU & GPU & Speedup \\
\midrule
Classical CNN & C32-P4-C64-P4-FC512 & 210 & 31 & 6.77x \\
Proposed graph CNN & GC32-P4-GC64-P4-FC512 & 200 & 25 & 8.00x \\
\bottomrule \end{tabular}
\caption{Time to process a mini-batch of 100 MNIST images. That is the total
training time divided by the number of gradient steps.} 
\label{tab:speedup}
\end{table*}

\begin{figure}[h!]
\vspace{0.5cm}
\centering
\includegraphics[width=7cm]{images/speed.png}
\caption{Training time over a mini-batch of 100 20NEWS documents w.r.t. $n$, the
number of selected words, for the three considered filters. The architecture is
GC32 with $K=5$ for Spline and Chebyshev.}
\label{fig:runtime}
\end{figure}

@@

\begin{table*}[h!]
\vspace{0.5cm}
\centering
\begin{tabular}{lcc} \toprule
Architecture & 8-NN on 2D Euclidean grid & random \\
\midrule
GC32 & 97.40 & 96.88 \\
GC32-P4-GC64-P4-FC512 & 98.65\todo{99.14} & 95.39 \\
\bottomrule \end{tabular}
\caption{Classification accuracies with different graph constructions on MNIST.} 
\label{tab:mnist_quality}
\end{table*}

@@

\begin{table*}[h!] \centering
\vspace{0.5cm}
\begin{tabular}{ccccc} \toprule
& \multicolumn{2}{c}{word2vec} & & \\
bag-of-words & pre-trained & learned & approximate & random \\
\midrule
67.50 & \todo{66.98} & 68.26 & 67.86 & 67.75 \\
\bottomrule \end{tabular}
\caption{Classification accuracies of GC32 with different graph constructions on 20NEWS.} 
\label{tab4b}
\label{tab:20news_quality}
\end{table*}

>>>>

%\newpage
The compositional local stationarity property of CNNs can be efficiently
implemented on regular grids, like image and sound domains, as convolutional, 
downsampling and pooling operators are mathematically well-defined on such discretized
Euclidean spaces. This has led to the breakthrough of CNNs in image, video, and
sound recognition tasks \cite{art:LeCunBengioHinton15DL} as these data lie on
low-dimensional regular lattices. But not all data lie on regular grids. User
data on social networks, gene data on biological regulatory networks, log data
on telecommunication networks, or text documents on words' embedding are
important examples of data lying on irregular or non-Euclidean domains.
Unfortunately, CNNs cannot be directly applied to such complex domains.% as the building blocks of CNNs, convolution, downsampling, and pooling, are only defined for regular grids.

%A generalization to irregular grids is not straightforward as the building blocks of CNNs, convolution, downsampling, and pooling, are only defined for regular grids.

A generalization to irregular grids is not straightforward as the standard operators of convolution, downsampling, and pooling, are only defined for regular grids. This makes this extension challenging, both theoretically and implementation-wise. This work leverages the recent works of
\cite{pro:GregorLeCun10LRF, pro:CoatesNg11LRF,
art:BrunaZarembaSzlamLeCun13DLgraphs, art:HenaffBrunaLeCun15DLgraphs,
art:HammondVandergheynstGribonval11GraphWav,
art:ShumanNarangFrossardOrtegaVandergheynst13ReviewSPG} to introduce an
efficient implementation of CNNs on irregular domains represented here as
graphs. Graphs are universal representations of heterogeneous pairwise
relationships between possibly high-dimensional data. Graphs can encode complex
geometric structures, and can be studied with strong mathematical tools such as
spectral graph theory \cite{book:Chung97Spectral}, a blend between graph theory and harmonic analysis.

@@

\begin{table*}[h!]
\centering
\begin{tabular}{llc}
\toprule
Model & Architecture & Accuracy \\
\midrule
%Linear SVM & 91.76  \\
%Softmax & 92.36  \\
Classical CNN & C32-P4-C64-P4-FC512 & \textbf{99.33}  \\
Proposed graph CNN & GC32-P4-GC64-P4-FC512 & 99.14  \\
\bottomrule
\end{tabular}
\caption{Classification accuracies for the proposed model and a classical CNN on
MNIST.} 
\label{tab:mnist}
\end{table*}

@@

\begin{table*}[h!] \centering
\begin{tabular}{lc} \toprule
Model & Accuracy \\
\midrule
Linear SVM & 65.90 \\
Multinomial Naive Bayes & 68.51 \\
%Multinomial logistic regression (softmax) & 66.28 \\
Softmax & 66.28 \\
\addlinespace
FC2500 & 64.64 \\
FC2500-FC500 & 65.76 \\
\addlinespace
GC32 & 68.26 \\
%GC32-FC500 & \todo{?} \\
\bottomrule \end{tabular}
\caption{Classification accuracies for the proposed model and a other algorithms
on 20NEWS.} 
\label{tab:20news}
\end{table*}

20NEWS consists of 18,846 (11,314 for training and 7,532 for testing) text
documents associated with 20 classes \cite{art:Joachims9620NEWS}. We extracted
the 10,000 most common words from the 93,953 unique words in this corpus. Each
document is represented using the bag-of-words model, normalized across words.
To test our model, we constructed a 16-NN graph of the word2vec
\cite{pro:MikolovChenCorradoDean13word2vec} embedding of those words, which
produced a graph of $n = |\V| = 10,000$ nodes and
$|\E| = 132,834$ edges.  All CNN models were trained for 20 epochs by the Adam
optimizer \cite{art:KingmaBa14AdamOpt} with a learning rate of 0.1, without regularization nor
dropout. The filter support was set to $K = 5$.

@@

\begin{table*}[h!] \centering
\begin{tabular}{llccc} \toprule
& & \multicolumn{3}{c}{Accuracy} \\
\cmidrule{3-5}
Dataset & Architecture & Non-Param \eqnref{filt_non-param} &
Spline \eqnref{filt_spline} \cite{\bruna} &
Chebyshev \eqnref{filt_cheby} \\
\midrule
MNIST & GC10 & 95.75 & 97.26 & \textbf{97.48} \\
MNIST & GC32-P4-GC64-P4-FC512 & 96.28 & 97.15 & \textbf{99.14} \\
%20NEWS & GC32 & \todo{?} & \todo{?} & \todo{?} \\
\bottomrule \end{tabular}
\caption{Comparison of accuracy results for different types of spectral filters.
Spline and Chebyshev filters use $K=25$.} % \todo{$K=5$ for 20NEWS}
\label{tab:filters}
\end{table*}

@@

\begin{table*}[ht] \centering
\begin{tabular}{llccc} \toprule
& & \multicolumn{2}{c}{Time (ms)} & \\
Model & Architecture & CPU & GPU & Speedup \\
\midrule
Classical CNN & C32-P4-C64-P4-FC512 & 210 & 31 & 6.77x \\
Proposed graph CNN & GC32-P4-GC64-P4-FC512 & 200 & 25 & 8.00x \\
\bottomrule \end{tabular}
\caption{Time to process a mini-batch of 100 MNIST images. That is the total
training time divided by the number of gradient steps.} 
\label{tab:speedup}
\end{table*}

\begin{figure}[ht]
\centering
\vspace{-20pt}
\includegraphics[width=\textwidth]{images/runtime_crop}
\caption{Training time over a mini-batch of 100 20NEWS documents w.r.t. $n$, the
number of selected words, for the three considered filters. The architecture is
GC32 with $K=5$ for Spline and Chebyshev.}
\label{fig:runtime}
\end{figure}

@@

\begin{table*}[h!]
\centering
\begin{tabular}{lcc} \toprule
Architecture & 8-NN on 2D Euclidean grid & random \\
\midrule
GC32 & 97.40 & 96.88 \\
GC32-P4-GC64-P4-FC512 & 99.14 & 95.39 \\
\bottomrule \end{tabular}
\caption{Classification accuracies with different graph constructions on MNIST.} 
\label{tab:mnist_quality}
\end{table*}

@@

\begin{table*}[h!] \centering
\begin{tabular}{ccccc} \toprule
& \multicolumn{2}{c}{word2vec} & & \\
bag-of-words & pre-trained & learned & approximate & random \\
\midrule
67.50 & 66.98 & 68.26 & 67.86 & 67.75 \\
\bottomrule \end{tabular}
\caption{Classification accuracies of GC32 with different graph constructions on 20NEWS.} 
\label{tab4b}
\label{tab:20news_quality}
\end{table*}
